Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2020-11-16 GWLDCI.tex
dealt with the standard facts, still not perfect bit it should do

\begin{proof}
Let us first record a few standard facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).  If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.  No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\todo{Referee Y wants a ref for these standard things.}

>>>>

\begin{proof}
Let us first record a few elementary facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).  If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.  No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations\cite{MPhD}, then the earlier facts follow from Euler's formula for planar graphs.}
